\textsf{Are large language models superhuman chemists?}

### 2024-10-29 src/tex/appendix.tex
Update appendix.tex

Based on these findings, some scope for improving these models could be to focus on enhancing knowledge-based training, possibly through improved pre-training on chemistry-specific texts or with chemistry knowledge-base integration. However, this type of knowledge should be integrated with sound machine-learning approaches. For example, \GalacticaOneTwentyB showed the lowest performance in our study, even though it was specifically trained on scientific text. This suggests that the knowledge embedded in papers and textbooks has not been fully leveraged.

>>>>

Based on these findings, some scope for improving these models could be to focus on enhancing knowledge-based training, possibly through improved pre-training on chemistry-specific texts or with chemistry knowledge-base integration. However, this type of knowledge should be integrated with sound machine-learning approaches. For example, even \PaperQATwo could not outperform the \gls{llm} using the tools, even though the model now would have access to literature evidence. This suggests we might need an overhaul of how we approach agent building, and how we train models for science applications, since clearly the valuable information stored in textbooks and papers, that can be used to answer questions is not fully leveraged by any of the state-of-the-art models and systems.
